### 2020-11-19 doc/manuscript/Dow_manuscript.Rmd

We fit the model of @mcmahon_general_2015 to define *phenological dates and growth rates* (Fig. `r schematic`). 
...DETAILS...

>>>>

We fit the model of @mcmahon_general_2015 to define *phenological dates and growth rates* (Fig. `r schematic`). This 5 parameter logistic model was fitted to each tag year's dendroband measurements in R: L + ((K - L) / (1 + 1/theta * exp(-(r * (doy - doy_ip) / theta)) ^ theta))
Where L and K are lower and upper asymptotes of the model, theta is a tuning parameter controlling the slope of the curve toward the upper asymptote, r is the slope of the curve at the inflection point, doy_ip is the day of year where the inflection point occurs, and doy are the modeled days of year, in this case, 1-365. *We note that the maximum growth rate does not always occur on the doy_ip, and is controlled magically by theta somehow.* Using the optimized parameters for each tree year, we could then determine the DBH on every day within that year, giving us the ability to extract the intra-annual growth variables we were interested in.
